Associations of severe COVID-19 with polypharmacy in the REACT-SCOT case-control study (draft only, not to be quoted)

### 2020-06-16 pharmaco.Rmd
last commit before new linkage

>>>>

```{r timewin.opiate, echo=FALSE, warning=FALSE, message=FALSE}

knitr::kable(table.timewindow.opiate,
             escape=FALSE,
             label="timewindow.opiate", 
             booktabs=TRUE,
             col.names=c(clean.header(colnames(table.timewindow.opiate)[1:2]), 
                         "Rate ratio (95\\% CI)", "$p$-value"),
             caption=paste0("Associations of severe disease with dispensed prescriptions for opiate analgesics by ", TW, "-day time window")) %>%
	column_spec(column=1, width="3cm") %>%
	column_spec(column=2:3, width="2cm") %>%
	column_spec(column=4, width="2.5cm") %>%
	column_spec(column=5, width="1.5cm") %>%
    kable_styling(latex_options="hold_position")
